\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-25 coqimpl.tex
Adding example for CoqImpl.

\textbf{Family compiled into module.} This is the main idea of compiling
family components into Coq's primitives: we compile families into Coq
modules, family types into module types, and the context of a given term
into parameters of the module. Unlike module, we need to faithfully
reflect the \textit{late binding} nature of families: for each defining
field $ .. \cL\sigma \vdash t : T $, we need to compile $t$ using
``universal-quantifier-wrapped term'' : $.. \vdash \lambda t : \forall
\cL \sigma. T$. However, instead of using Coq's universal quantifier, we
choose module and module parameters to achieve this wrapping---each
family type in the context of the judgement will be one module parameter
with the compiled module type, and thus each field of the family will
compile into a functor parametrized by its context. Doing so we can also
get rapid feedback from type checking when the users are defining each
field interactively with Coq.
% Insert one pseudo-code example for explanation of the mechanism
\begin{figure}[!htb]
  \begin{minipage}[t]{0.25\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Family A.
Field a : nat 
  := 1.
Field b : a = a
  := eq_refl.
Final Field a' : nat 
  := 1. 
Field b' : a' = 1
  := eq_refl.
EndFamily.
\end{minted}
  \end{minipage}%\YZ{Can the self's be omitted?}\EDJreply{Yes. But in our current plugin implementation it is not omitted. I think altering example is fine. If you think some small distance between example and the current implementation is fine, please comment back and I will remove all the self_}\YZreply{If omitting the self's poses no technical challenges, then I'd say it's fine to also omit them in this figure.}\EDJreply{Omitting self_ is easy and not much engineering effort is required. But omitting self_ will lead to `A.a' instead of `a' actually. So if we really want `a' as you last time mentioned, then a resolution is required and more engineering effort is required. But I don't see any technical difficulties. I have removed all the self, please check.}
  \begin{minipage}[t]{0.4\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module a_4 (self_A: EmptySig).
Definition a : nat := 1. End a_4.
Module Type a_5 (self_A: EmptySig).
Parameter (a : nat). End a_5.
Module Type a_6 := a_5 EmptyMod.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.3\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module b_7 (self_A: a_6).
Definition b 
  : self_A.a = self_A.a 
  := eq_refl. End b_7.

@@

% Concrete details of compilation of a family term data structure
Taking \cref{fig:plugin-example1} as an example: when the user
interactively inputs the line "Field a : nat := ..", our plugin will
translate this statement into the "Module a_4", "Module Type a_5, a_6"
three components.
{The "EmptySig" is just empty module type.} Then,
these modules and module types will be generated and type-checked by Coq
immediately. The compiled "Module a_4" is then part of the context of
"Field b" (as the module type of "self_A") for "b" to refer to. The
internal representation of family "A" is the list of these
compiled modules and module types. We can achieve incremental
checking and overriding as in \ref{langdesign-req0}---for example, if we
want to override "Field a", we simply replace that compiled module with
the new module inside the list. This compiled module type serves as an
abstraction that enables overriding.

Now that we know a family declaration is compiled to a list of Coq
modules and module types, we may want to aggregate them into one complete compiled
module.\YZ{The reader wonders why this aggregation is needed. Seems like the place to talk about how the programmer can use A outside Family A.}
We achieve that by repeatedly using Coq's "Include" command as
the example illustrates. Note that, in our example, we include two
functors without arguments---this is due to a peculiarity of Coq's
"Include": non-instantiated parameters will be automatically
instantiated by the appropriate fields in the surrounding defining
module.
For example, "b_7" requires a module of type "a_6". Inside module "A",
when "Include a_4" is done, we will have a field \mintinline{Coq}{a : nat}
inside the current surrounding "A". Then when we
\mintinline{Coq}{Include b_7} without specifying the module parameter,
Coq will try to find fields in the surrounding module (i.e., module
"A") to instantiate \mintinline{Coq}{self_A: a_6}. This is satisfied by
the \mintinline{Coq}{a : nat} that is included earlier.
The resulting compiled module is just like mundane Coq's module and thus maintains all the computational mechanism from Coq, fulfilling \ref{langdesign-req0b}.

% explaining inheritance
Besides standalone family, we also need to implement family inheritance.
To simplify the implementation, we can consider all families as
inheritance and the standalone families are extending the empty family.
Thus we need to deal with only inheritance during interactive proving.

An inheritance data\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.}\YZreply{I think this is the place where you can use an example to demonstrate these three kinds of inheritance.}
will be annotated with the type for the input family
and output family. There are three kinds of inheritance---extend,
override, and inherit. Extending corresponds to adding new fields,
overriding corresponds to modifying existent fields, and inheriting
corresponds to directly taking fields from the parent.
Thus, it is possible to consider inheritance as solely a data rather
than a functor, and this actually provides us the possibility to
\text{mix-in} inheritance data.

\textbf{Reasoning Requires Non-Overridable.}\YZ{At this point in this section, overriding has not been discussed yet, but it is already discussing non-overridables. Should probably discuss the extensibility first.}
This compilation strategy
can allow fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, there are cases where we need to expose
the concrete definition of a given field (especially when we are proving
properties about it).

For example, we may
define $"add" : \mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ as one field
and intend to prove its commutativity in a following field $"comm"$.
But to prove so, we need to know more than just a type interface of
"add" but also its \textbf{concrete fixpoint definition}. Otherwise, in the
future, once "add" is overridden into a subtraction function then
"comm" will have problem to be inherited.\YZ{The sentence reads as if you want to enable overriding "add", whereas what you really want is to expose the definition equality about "add".}
A more concrete example is in \cref{fig:plugin-example1}, consider the
case we have "Field b : a = 1 := .." instead. Then our
compilation and Coq's type checking will both fail: in the context of
"b" (module type "a_6") we only know "a" is of type "nat" but nothing
more (and this is necessary so that "a" can be overridden in the
future).\YZ{Not clear if you want to be able to override a or want to be able to have 'Field b : a = 1'.}

To fix that, we need more information on "a" than its type---we
need to expose the concrete definition "a = 1" to the context of "b".
%\YZ{I had a hard time working through these two paras. I guess they are
%saying that there is a need to expose definitional equalities, and
%therefore we need non-overridables. This causal flow should be made
%more explicit.}\EDJreply{Good suggestion. I try to add this casual flow into the first line of the paragraph. Please check and resolve if find satisfied.}

@@

\textbf{Special Fields: Overridable and Sealed Family as Interface.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases where overriding and
equational reasoning are both needed, especially when we use Coq to do
computation. For example, we may want a field to be an overridable 
monotonic function. We cannot split into two fields
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f},
because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism---we allow the
users to specify the compiled module type of a given family,\YZ{I don't understand "specify the family/compiled module type"}\EDJreply{Sorry. I rephase it into "compiled module type of a given family".}\YZreply{Still cannot see what is going on and how it is related to the sentence that follows. An example is due.}
and thus we can have a
\textit{locally transparent}, \textit{non-overridable} field located in
an \textit{overridable} family. Using the above example, we simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family.

``Sealed'' families can actually simulate interfaces in certain sense\YZ{I was actually thinking sealed families simulate sigma types, no?}\EDJreply{You are absolutely right. I should add a "can" here. I can use sealed family to simulate interface is by creating a sigma type, but making the implemntation of sigma type trivial (using place holder/using axiom as I specified below). Then once I want to instantiate with real implementation, I override the whole family -- as long as it has the same type as the sealed family, everything still works.}\YZreply{Can you explain this with an example? I recall the AbsInt example uses it?}---we can assign each field of the sealed family with \mintinline{Coq}{Axiom non_implement : forall {T : Type}, T.}, and later instantiate them with concrete implementation by overriding this family.\YZ{I don't understand what it means to "assign each field with an axiom".}\EDJreply{It really means ``place holder'' in general programming language (Python's NonImplement()), defer to future. Because Coq's Axiom can be used to instantiate anything.}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

>>>>

\textbf{Family compiled into module.} This is the main idea of compiling
family components into Coq's primitives: we compile families into Coq
modules, family types into module types, and the context of a given term
into parameters of the module. Unlike module, we need to faithfully
reflect the \textit{late binding} nature of families: for each defining
field $ .. \cL\sigma \vdash t : T $, we need to compile $t$ using
``universal-quantifier-wrapped term'' : $.. \vdash \lambda t : \forall
\cL \sigma. T$. However, instead of using Coq's universal quantifier, we
choose module and module parameters to achieve this wrapping---each
family type in the context of the judgement will be one module parameter
with the compiled module type, and thus each field of the family will
compile into a functor parametrized by its context. Doing so we can also
get rapid feedback from type checking when the users are defining each
field interactively with Coq.
% Insert one pseudo-code example for explanation of the mechanism
\begin{figure}[!htb]
  \begin{minipage}[t]{0.25\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Family A.
Field a : nat 
  := 1.
Field b : a = a
  := eq_refl.
Final Field a' : nat 
  := 1. 
EndFamily.
\end{minted}
  \end{minipage}%\YZ{Can the self's be omitted?}\EDJreply{Yes. But in our current plugin implementation it is not omitted. I think altering example is fine. If you think some small distance between example and the current implementation is fine, please comment back and I will remove all the self_}\YZreply{If omitting the self's poses no technical challenges, then I'd say it's fine to also omit them in this figure.}\EDJreply{Omitting self_ is easy and not much engineering effort is required. But omitting self_ will lead to `A.a' instead of `a' actually. So if we really want `a' as you last time mentioned, then a resolution is required and more engineering effort is required. But I don't see any technical difficulties. I have removed all the self, please check.}
  \begin{minipage}[t]{0.4\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module a_4 (self_A: EmptySig).
Definition a : nat := 1. End a_4.
Module Type a_5 (self_A: EmptySig).
Parameter (a : nat). End a_5.
Module Type a_6 := a_5 EmptyMod.
\end{minted}
  \end{minipage}
  \begin{minipage}[t]{0.3\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Module b_7 (self_A: a_6).
Definition b 
  : self_A.a = self_A.a 
  := eq_refl. End b_7.

@@

% Concrete details of compilation of a family term data structure
Taking \cref{fig:plugin-example1} as an example: when the user
interactively inputs the line "Field a : nat := ..", our plugin will
translate this statement into the "Module a_4", "Module Type a_5, a_6"
three components.
{The "EmptySig" is just an empty module type.} Then,
these modules and module types will be generated and type-checked by Coq
immediately. The compiled "Module a_4" is then part of the context of
"Field b" (as the module type of "self_A") for "b" to refer to. The
internal representation of family "A" is the list of these
compiled modules and module types. We can achieve incremental
checking and overriding as in \ref{langdesign-req0}---for example, if we
want to override "Field a", we simply replace that compiled module with
the new module inside the list. This compiled module type serves as an
abstraction that enables overriding.

Once the user closes a family with "EndFamily", they can access its fields by using module syntax. For example, they can access "A.a" to get "1" after "Family A" is defined. This is achieved by a complete compilation from a family to a module, via aggregating the list of the modules in the internal representation: the plugin will repeatedly using Coq's "Include" command as the "Module A" in \cref{fig:plugin-example1} illustrates. Now, the user can use "Module A" anywhere as they are using "Family A".
\YZ{The reader wonders why this aggregation is needed. 
Seems like the place to talk about how the programmer can use A outside Family A.}

Note that, in our example, we include two
functors without arguments---this is due to a peculiarity of Coq's
"Include": non-instantiated parameters will be automatically
instantiated by the appropriate fields in the surrounding defining
module.
For example, "b_7" requires a module of type "a_6". Inside module "A",
when "Include a_4" is done, we will have a field \mintinline{Coq}{a : nat}
inside the current surrounding "A". Then when we
\mintinline{Coq}{Include b_7} without specifying the module parameter,
Coq will try to find fields in the surrounding module (i.e., module
"A") to instantiate \mintinline{Coq}{self_A: a_6}. This is satisfied by
the \mintinline{Coq}{a : nat} that is included earlier.
The resulting compiled module is just like mundane Coq's module and 
thus maintains all the computational mechanism from Coq, fulfilling \ref{langdesign-req0b}.

\begin{figure}[!htb]
  \begin{minipage}[t]{0.45\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Family I.
Field a : nat := 1.
Field b : a = a := eq_refl.
Fail Field c : a = 1 := eq_refl. (*Fail 1*)

Final Field a' : nat := 1.
Field c : a = 1 := eq_refl.
Field add : nat -> nat -> nat := (+).
Fail Field comm_add : ...

Family MonotonicF.
  Final Field f : nat -> nat := non_impl.
  Field p : monotonic f := non_impl.
SealFamily.

EndFamily.
\end{minted}
  \end{minipage}
\begin{minipage}[t]{0.45\linewidth}
\begin{minted}[fontsize=\footnotesize]{Coq}
Family I2 extends I.
Override Field a : nat := 1. (* Override *)
Inherit b.                   (* Inherit  *)

Field d : nat := a.          (* Extend   *)
Fail Override Field a' : nat := 2. (*Fail 2*)

Override Field add := (-).

Inherits Until MonotonicF.
Override Family MonotonicF.
  Final Field f : nat := (+ 1).
  Field p : monotonic f := ...
SealFamily. 
EndFamily.
\end{minted}
  \end{minipage}
  \caption{Example Code for Inheritance and Reasoning}\label{fig:plugin-example3}
\end{figure}

% explaining inheritance
Besides standalone family, we also need to implement family inheritance.
To simplify the implementation, we can consider all families as
inheritance and the standalone families are extending the empty family.
Thus we only need to deal with inheritance during interactive theorem proving.

There are only three kinds of inheritance we are dealing with---extend, override, and inherit. We use first-order data to encode inheritance data inside the implementation of the plugin. The inheritance data will include the information of (1) the ``type'' of the parent family, (2) a list of operation indicating how each field of the parent will be dealt with (either inherited or overrided), (3) the operations indicating newly extended fields, and (4) the ``type'' of the children family.\YZ{what is 'inheritance data'?}\EDJreply{It is just inheritance judgement, but before meta-theory is introduced, I can only say some "first-order data that represent the information of inheritance". I emphasize first order to distinguish from functor in ML community.}\YZreply{I think this is the place where you can use an example to demonstrate these three kinds of inheritance.} The surface syntax for the three kinds of inheritance are demonstrated in \cref*{fig:plugin-example3}. The implementation of overriding, inheritance, and extension is achieved by simply manipulating the internal representation of a family correspondingly---we can swap the module in the list for overriding, retain the module in the list for inheritance and add new module into the list for extension. The compilation from a family (internal representation) to a module still acts the same.

Since it is possible to consider inheritance as solely a first-order data rather
than a higher-order functor, it is actually plausible to
\text{mix-in} two inheritance data -- by carefully ``mix'' the internal list.

\textbf{Reasoning Requires Non-Overridable.}\YZ{At this point in this section, overriding has not been discussed yet, but it is already discussing non-overridables. Should probably discuss the extensibility first.}
This compilation strategy
has already allowed fields to be type-dependent on former fields thus fulfilling
\ref{langdesign-req1}. However, the current implementation is not satisfactory enough. There are cases where we need to expose
the concrete definition of a given field (especially when we are proving
properties about it).

% For example, we may
% define $"add" : \mathbb{Z} \to \mathbb{Z} \to \mathbb{Z}$ as one field
% and intend to prove its commutativity in a following field $"comm"$.
% But to prove so, we need to know more than just a type interface of
% "add" but also its \textbf{concrete fixpoint definition}. Otherwise, in the
% future, once "add" is overridden into a subtraction function then
% "comm" will have problem to be inherited.\YZ{The sentence reads as if you want to enable overriding "add", whereas what you really want is to expose the definition equality about "add".}
% A more concrete example is in \cref{fig:plugin-example1}, consider the
% case we have "Field b : a = 1 := .." instead. Then our
% compilation and Coq's type checking will both fail: in the context of
% "b" (module type "a_6") we only know "a" is of type "nat" but nothing
% more (and this is necessary so that "a" can be overridden in the
% future).
Take the field "c" in "Family I" in \cref{fig:plugin-example3} as the example, we can see that the first attempt of proving "a = 1" fails. This should fail, actually---because we want to retain the possibility to override "a" in the future, but the mere existence of the field "c" will stop that, since "c" witnesses "a" fix to "1". From the other perspective, the proof of "c" will require a concrete definition of "a" instead of just the exposure of its type. \textbf{We can see a conflict between \textit{overridable} and \textit{(definition-relevant) reasoning}}.  We enable the exposure of the concrete definition by providing "Final" keyword upon "a'".

This example might sounds trivial and non-practical. Let's look at the example field "add". Now that we only expose the type of "add", we cannot prove its commutativity in "comm_add" (because we don't have access to its concrete definition) but we can override "add" with subtraction function in "Family I2". This makes sense because we shouldn't have (inherited) commutativity property for subtraction anyway. This is contrary to how "a'" is declared "Final", the second "c" can prove that it's equal to 1 but "a'" is not overridable in the "Family I2".
\YZ{Not clear if you want to be able to override a or want to be able to have 'Field b : a = 1'.}\EDJreply{Rephrased. Please Check.}

% To fix that, we need more information on "a" than its type---we
% need to expose the concrete definition "a = 1" to the context of "b".
%\YZ{I had a hard time working through these two paras. I guess they are
%saying that there is a need to expose definitional equalities, and
%therefore we need non-overridables. This causal flow should be made
%more explicit.}\EDJreply{Good suggestion. I try to add this casual flow into the first line of the paragraph. Please check and resolve if find satisfied.}

@@

\textbf{Special Fields: Overridable/Sealed Family Simulating Sigma Type.} 
Non-overridable fields are still not expressive enough to achieve the full
extent of dependent type programming. There are cases where overriding and
(definition-relevant) reasoning are both needed. For example, we may want a field to be an overridable monotonic function. We cannot split into two fields
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f},
because to provide
"p" we need to have concrete definition of "f" in the family type, which
makes "f" non-overridable at all. One option is to use sigma type
\mintinline{Coq}{{f | monotonic f}}, but that can be cumbersome when we have
a bundle of stuff with multiple refinements.

To resolve this, we provide family sealing mechanism to simulate sigma type---we allow the
users to specify the compiled module type of a given family,\YZ{I don't understand "specify the family/compiled module type"}\EDJreply{Sorry. I rephase it into "compiled module type of a given family".}\YZreply{Still cannot see what is going on and how it is related to the sentence that follows. An example is due.}\EDJreply{Done. Please check.}
and thus we can have a
 \textit{non-overridable} (thus locally transparent) field located in
an \textit{overridable} family. Check the "MonotonicF" in \cref{fig:plugin-example3}, we simply seal
\mintinline{Coq}{f : nat → nat} and \mintinline{Coq}{p : monotonic f}
together inside an overridable family that does not allow "f"
to be overridden in any of its derived families.
Because "f" is non-overridable inside the family, its definition is
transparent and can be used to prove "p".
However, because the enclosing family of "f" is overridable, to swap the
implementation of "f", we just override the whole ``sealed'' family, like we do in "I2.MonotonicF".

In our example, the seal family "I.MonotonicF" is actually simulating interfaces as well\YZ{I was actually thinking sealed families simulate sigma types, no?}\EDJreply{You are absolutely right. I should add a "can" here. I can use sealed family to simulate interface is by creating a sigma type, but making the implemntation of sigma type trivial (using place holder/using axiom as I specified below). Then once I want to instantiate with real implementation, I override the whole family -- as long as it has the same type as the sealed family, everything still works.}\YZreply{Can you explain this with an example? I recall the AbsInt example uses it?}\EDJreply{Done. Please check.}. We have \\ ``\mintinline{Coq}{Axiom non_impl : forall {T : Type}, T.}'', and we have assigned it to both "f" and "p", and later instantiate in "I2" with concrete implementation by overriding this family "I.MonotonicF".  \YZ{I don't understand what it means to "assign each field with an axiom".}\EDJreply{It really means ``place holder'' in general programming language (Python's NonImplement()), defer to future. Because Coq's Axiom can be used to instantiate anything.}
% Basically, {a : int -> int; property : a is monotonic}, in this case
%   we may want to override "a" using different computation, but we still wnat
%   this refinement/property

### 2022-06-25 lang-design.tex
Adding example for CoqImpl.

\subsection{Language Design}
Inspired by our above requirements and Family Polymorphism, we propose
the following extension to Coq's Vernacular Commands.
% basically write down the specification of surface Coq commandline
%   and then explain  how the language design makes the programmer’s life easier
\begin{align*}
  V := \quad &"Family"~\langle ident\rangle~["extends"~\langle ident\rangle] 
  \quad |\quad "EndFamily" \\
  & |\quad "FRecursor"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle~"using"~\langle ident\rangle \\
  & |\quad "Extend"~"Family"~\langle ident\rangle \\ 
  & |\quad ["Extend"]~"FInductive"~\langle ident\rangle \\ 
  & |\quad ["Final" | "Override"]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & | \quad "Inherit"~\langle ident\rangle \quad | \quad "Inherit Until"~\langle ident\rangle
\end{align*}

We use "Family" and "EndFamily" to scope, and "Field" is used to declare new members in a family.
We can define nested families.
Family will also be used to encode recursive handlers. Each case
handling of one inductive type will be aggregated into one family, then
"FRecursor" will be used to construct a recursor using these handlers.
For example, \mintinline{Coq}{FRecursor recur about T motive f} "using"
"handlers" will generate a new field "recur" that is doing induction
(using elimination principle of "T") using motive "f", and the handlers
are located in the family "handlers".

>>>>

\subsection{Language Design}
Inspired by our above requirements and Family Polymorphism, we propose
the following extension to Coq's Vernacular Commands.
% basically write down the specification of surface Coq commandline
%   and then explain  how the language design makes the programmer’s life easier
\begin{align*}
  V := \quad &"Family"~\langle ident\rangle~["extends"~\langle ident\rangle] 
  \quad |\quad "EndFamily" \\
  & |\quad "FRecursor"~\langle ident\rangle~"about"~\langle ident\rangle~"motive"~\langle term\rangle~"using"~\langle ident\rangle \\
  & |\quad "Extend"~"Family"~\langle ident\rangle \\ 
  & |\quad ["Extend"]~"FInductive"~\langle ident\rangle \\ 
  & |\quad ["Final" | "Override"]~"Field"~\langle ident\rangle~":"~\langle term \rangle~":="~\langle term \rangle \\
  & | \quad "Inherit"~\langle ident\rangle \quad | \quad "Inherit Until"~\langle ident\rangle \quad | \quad ...
\end{align*}

These are some core extension we proposed to support \cref{fig:STLC-example}. We use "Family" and "EndFamily" to scope, and "Field" is used to declare new members in a family.
We can define nested families.
Family will also be used to encode recursive handlers. Each case
handling of one inductive type will be aggregated into one family, then
"FRecursor" will be used to construct a recursor using these handlers.
For example, \mintinline{Coq}{FRecursor recur about T motive f} "using"
"handlers" will generate a new field "recur" that is doing induction
(using elimination principle of "T") using motive "f", and the handlers
are located in the family "handlers".
